# functions and graphs

## modulus function

$$|f(x)|=\begin{cases} 
  -f(x) & ,f(x)\lt{}0 \\
  f(x) & ,f(x)\geq{}0 
\end{cases}$$

it can also be represented as $|x|=\sqrt{x^2}$

```{r echo=FALSE}
desmos("f(x)=x^2-4$\\sqrt{f(x)^2}")
```

## conic sections

### circles

$$(x-h)^2+(y-k)^2=r^2$$

circle with center $(h,k)$ and radius $r$

```{r echo=FALSE}
desmos("(x-h)^2+(y-k)^2=l^2$h=-2$k=-1$l=4")
```

### ellipses

$$(\frac{x-h}{a})^2+(\frac{y-k}{b})^2=1$$

ellipse with center $(h,k)$, width $2a$ and height $2b$

```{r echo=FALSE}
desmos("((x-h)/a)^2+((y-k)/b)^2=1$h=2$k=2$a=4$b=2")
```

### hyperbolas

$$(\frac{x-h}{a})^2-(\frac{y-k}{b})^2=1$$
$$-(\frac{x-h}{a})^2+(\frac{y-k}{b})^2=1$$

asymptotes: $y=\pm\frac{b}{a}(x-h)+k$

```{r echo=FALSE}
desmos("((x-h)/a)^2-((y-k)/b)^2=1$-((x-h)/a)^2+((y-k)/b)^2=1$h=0$k=1$a=4$b=2")
```

## inverse circular functions

| function     | domain             | range                            |
| ------------ | ------------------ | -------------------------------- |
| $\arcsin(x)$ | $[0,1]$            | $[-\frac{\pi}{2},\frac{\pi}{2}]$ |
| $\arccos(x)$ | $[0,1]$            | $[0,\pi]$                        |
| $\arctan(x)$ | $[-\infty,\infty]$ | $[-\frac{\pi}{2},\frac{\pi}{2}]$ |

```{r echo=FALSE}
desmos("f(x)=\\arcsin(x)$g(x)=\\arccos(x)$h(x)=\\arctan(x)")
```

## parametric equations

$$x=f(t)$$
$$y=g(t)$$

use simultaneous equation to solve parametric equations

```{r echo=FALSE}
desmos("x=8\\cos(t)$y=8\\sin(t)$(8\\cos(t),8\\sin(t))$t=0")
```