# more functions

## power functions

```{r echo=FALSE}
desmos("f(x)=x^2$g(x)=x^3$h(x)=x^4")
```

```{r echo=FALSE}
desmos("i(x)=\\sqrt{x}$j(x)=\\sqrt[3]{x}")
```

```{r echo=FALSE}
desmos("k(x)=\\frac{1}{x}$l(x)=\\frac{1}{x^2}")
```

## exponentials and logarithms

### exponential functions

for $a\in{}R^+\setminus\{1\}$, the graph $y=a^x$ has the following properties:

- the y-axis intercept is 1
- the x-axis is an asymptote

```{r echo=FALSE}
desmos("f(x)=2^x$g(x)=e^x$h(x)=10^x")
```

| index laws               |                                   |
| ------------------------ | --------------------------------- |
| $x^a\times{}x^b=x^{a+b}$ | $x^a\div{}x^b=x^{a-b}$            |
| $(xy)^a=x^ay^a$          | $(\frac{x}{y})^a=\frac{x^a}{y^a}$ |
| $(x^a)^b=x^{ab}$         | $x^0=1$                           |

### logarithmic functions

for $a\in{}R^+\setminus\{1\}$, the graph $y=\log_ax$ has the following properties:

- the x-axis intercept is 1
- the y-axis is an asymptote

```{r echo=FALSE}
desmos("f(x)=\\log_2{x}$g(x)=\\log_e{x}$h(x)=\\log_{10}{x}")
```

| log laws                     |                                       |
| ---------------------------- | ------------------------------------- |
| $\log_am+\log_an=\log_a(mn)$ | $\log_am-\log_an=\log_a(\frac{m}{n})$ |
| $p\log_am=\log_a(m^p)$       | $-\log_am=\log_a(\frac{1}{m})$        |
| $\log_a1=0$                  | $\log_aa=1$                           |
| $\log_am=\frac{\log_em}{\log_ea}=\frac{\log_{10}m}{\log_{10}a}$ |    |

### exponential growth and decay

model for quantity growing/decaying at an exponential rate:

$A=A_0b^t$

- $A_0$ is the initial quantity
- $b=e^k$ is the rate constant (growth if $b>1$, decay if $b<1$)
- $t$ is time

cell growth - doubles every $T_D$ (unit of time):

$N=N_02^{\frac{t}{T_D}}$

- $N_0$ is the initial quantity
- $T_D$ is the generation time (how long it takes to double)
- $t$ is time

## circular functions

```{r echo=FALSE}
desmos("f(x)=\\sin(x)$g(x)=\\cos(x)$h(x)=\\tan(x)")
```