# polynomial functions

## what is it

a polynomial can have constants, variables and exponents, but never division by a variable. exponents of variables in polynomial are 0, 1, 2,.. (zero or positive integer number)

$$P(x)=a_nx^n+a_{n-1}x^{n-1}+...+a_1x+a_0$$

### degree

the degree of the polynomial is the largest exponent of that variable.

| name      | degree | rule                  |
| --------- | ------ | --------------------- |
| constant  | 0      | $a$                   |
| linear    | 1      | $ax+b$                |
| quadratic | 2      | $ax^2+bx+c$           |
| qubic     | 3      | $ax^3+bx^2+cx+d$      |
| quartic   | 4      | $ax^4+bx^3+cx^2+dx+e$ |

### general form

$$f(x)=ax^3+bx^2+cx+d$$

- easy to find y-intercept
- hard to graph

```{r echo=FALSE}
desmos("f(x)=a$g(x)=ax+b$h(x)=ax^2+bx+c$i(x)=ax^3+bx^2+cx+d$j(x)=ax^4+bx^3+cx^2+dx+e$a=-2$b=4$c=-2$d=3$e=-3")
```

### turning point form

$$f(x)=a(x-b)(x-c)(x-d)$$

- easy to find x-intercepts
- easy to graph

```{r echo=FALSE}
desmos("f(x)=a(x-b)$g(x)=a(x-b)(x-c)$h(x)=a(x-b)(x-c)(x-d)$i(x)=a(x-b)(x-c)(x-d)(x-e)$a=-2$b=0$c=-3$d=-4$e=-1")
```

## remainder theorem

if $P(x)$ is divided by $(ax+b)$ the remainder is $P(-\frac{b}{a})$

## factor theorem

if $P(-\frac{b}{a})=0$ then $(ax+b)$ is a factor

## formulas

### quadratic formula

$$\frac{-b\pm{}\sqrt{b^2-4ac}}{2a}$$

$f(x)=ax^2+bx+c$

if $f(x)=0$ then $x=\frac{-b\pm{}\sqrt{b^2-4ac}}{2a}$

the discriminant $\Delta=b^2-4ac$

- if $\Delta>0$ then the quadratic has 2 real solutions
- if $\Delta=0$ then the quadratic has 1 real solution
- if $\Delta<{}0$ then the quadratic has no real solutions

the vertex is at $(-\frac{b}{2a},f(-\frac{b}{2a}))$

### difference of squares

$$x^2-a^2=(x+a)(x-a)$$

### difference and sum of two cubes

$$x^3-a^3=(x-a)(x^2+ax+a^2)$$
$$x^3+a^3=(x+a)(x^2-ax+a^2)$$