# more functions

## power functions

```{r echo=FALSE}
desmos("f(x)=x^2$g(x)=x^3$h(x)=x^4")
```

```{r echo=FALSE}
desmos("i(x)=\\sqrt{x}$j(x)=\\sqrt[3]{x}")
```

```{r echo=FALSE}
desmos("k(x)=\\frac{1}{x}$l(x)=\\frac{1}{x^2}")
```

## exponentials and logarithms

### exponential functions

for $a\in{}R^+\setminus\{1\}$, the graph $y=a^x$ has the following properties:

- the y-axis intercept is 1
- the x-axis is an asymptote

```{r echo=FALSE}
desmos("f(x)=2^x$g(x)=e^x$h(x)=10^x")
```

| index laws               |                                   |
| ------------------------ | --------------------------------- |
| $x^a\times{}x^b=x^{a+b}$ | $x^a\div{}x^b=x^{a-b}$            |
| $(xy)^a=x^ay^a$          | $(\frac{x}{y})^a=\frac{x^a}{y^a}$ |
| $(x^a)^b=x^{ab}$         | $x^0=1$                           |

### logarithmic functions

for $a\in{}R^+\setminus\{1\}$, the graph $y=\log_ax$ has the following properties:

- the x-axis intercept is 1
- the y-axis is an asymptote

```{r echo=FALSE}
desmos("f(x)=\\log_2{x}$g(x)=\\log_e{x}$h(x)=\\log_{10}{x}")
```

| log laws                     |                                                                 |
| ---------------------------- | --------------------------------------------------------------- |
| $\log_a1=0$                  | $\log_aa=1$                                                     |
| $\log_am+\log_an=\log_a(mn)$ | $\log_am-\log_an=\log_a(\frac{m}{n})$                           |
| $p\log_am=\log_a(m^p)$       | $\log_am=\frac{\log_em}{\log_ea}=\frac{\log_{10}m}{\log_{10}a}$ |

### exponential growth and decay

model for quantity growing/decaying at an exponential rate:

$A=A_0b^t$

- $A_0$ is the initial quantity
- $b=e^k$ is the rate constant (growth if $b>1$, decay if $b<1$)
- $t$ is time

cell growth - doubles every $T_D$ (unit of time):

$N=N_02^{\frac{t}{T_D}}$

- $N_0$ is the initial quantity
- $T_D$ is the generation time (how long it takes to double)
- $t$ is time

## circular functions

```{r echo=FALSE}
desmos("f(x)=\\sin(x)$g(x)=\\cos(x)$h(x)=\\tan(x)")
```

### exact values

for $x\in{[0,\frac{\pi}{2}]}$

| function | $0$ | $\frac{\pi}{6}$      | $\frac{\pi}{4}$      | $\frac{\pi}{3}$      | $\frac{\pi}{2}$   |
| :------: | :-: | :------------------: | :------------------: | :------------------: | :---------------: |
| $\sin$   | $0$ | $\frac{1}{2}$        | $\frac{1}{\sqrt{2}}$ | $\frac{\sqrt{3}}{2}$ | $1$               |
| $\cos$   | $1$ | $\frac{\sqrt{3}}{2}$ | $\frac{1}{\sqrt{2}}$ | $\frac{1}{2}$        | $0$               |
| $\tan$   | $0$ | $\frac{1}{\sqrt{3}}$ | $1$                  | $\sqrt{3}$           | $\text{undefine}$ |

```{r echo=FALSE}
desmos("x^2+y^2=100$\\left(10\\cos\\left(t\\right),10\\sin\\left(t\\right)\\right)$t=0")
```

### symmetric properties

| $-x$                | $\pi-x$                | $\pi+x$                |
| ------------------- | ---------------------- | ---------------------- |
| $\sin(-x)=-\sin(x)$ | $\sin(\pi-x)=\sin(x)$  | $\sin(\pi+x)=-\sin(x)$ |
| $\cos(-x)=\cos(x)$  | $\cos(\pi-x)=-\cos(x)$ | $\cos(\pi+x)=-\cos(x)$ |
| $\tan(-x)=-\tan(x)$ | $\tan(\pi-x)=-\tan(x)$ | $\tan(\pi+x)=\tan(x)$  |

### complementary angles

| $\frac{\pi}{2}-x$               | $\frac{\pi}{2}+x$                |
| ------------------------------- | -------------------------------- |
| $\sin(\frac{\pi}{2}-x)=\cos(x)$ | $\sin(\frac{\pi}{2}+x)=\cos(-x)$ |
| $\cos(\frac{\pi}{2}-x)=\sin(x)$ | $\cos(\frac{\pi}{2}+x)=\sin(-x)$ |