# advance functions

## hybrid functions

$$f(x)=\begin{cases} 
  x+2 & x\leq0 \\
  -x^2+2 & 0<x\leq2 \\
  -2 & x>2 
\end{cases}$$

hybrid functions are functions that have different rules for different subsets of their domain

```{r echo=FALSE}
desmos("x+2\\left\\{x<0\\right\\}$-x^2+2\\left\\{0<x<2\\right\\}$-2\\left\\{x>2\\right\\}")
```

## inverse functions

the inverse function $f^{-1}(x)$ of a function $f(x)$ is the same as reflecting the the graph $y=f(x)$ over the line $y=x$

to find the inverse of a function $y=f(x)$ swap all $x$ and $y$

```{r echo=FALSE}
desmos("f(x)=x^2$x=f(y)")
```

## composite functions

a composite function $f(g(x))$ or $f\circ g(x)$ is a compose of a function inside another function

- $\text{range}(g(x))\in \text{domain}(f(x))$
- $\text{domain}(f\circ g(x))=\text{domain}(g(x))$

- a composite function can exist if the range of the inside function is a subset of the domain of the outer function
- the domain of the composite function is the domain of the inside function

```{r echo=FALSE}
desmos("f(x)=x^2$g(x)=x-2$y=f(g(x))")
```

## odd and even functions

### even function

an even function are function that are symmetrical about the $y$ axis

$$f(-x)=f(x)$$

```{r echo=FALSE}
desmos("f(x)=x^2$g(x)=\\cos{x}")
```

### odd function

an odd function are function that are rotationally symmetrical about the origin

$$f(-x)=-f(x)$$

```{r echo=FALSE}
desmos("f(x)=x^3$g(x)=\\sin{x}")
```